R dyntrace report

### 2018-02-02 graphs/report.Rmd
Fixed function aggregation, so that functions represented in multiple vignettes only get counted once.

``` {r, "basic info", include=FALSE}
basic_info <- 
  load_local_csv("basic_info.csv") %>%
  group_by(name) %>%
  summarise(
    datasets=paste(name, collapse=", "),
    n.datasets=n(),
    n.functions=sum(n.functions),
    n.calls=sum(n.calls),
    n.promises=sum(n.promises),
    n.promise.forces=sum(n.promise.forces),
    n.promise.lookups=sum(n.promise.lookups), 
    n.alien.promises=sum(n.alien.promises),
    n.alien.promise.forces=sum(n.alien.promise.forces)
  )

@@

aggregate_basic_info <- 
  basic_info %>% summarise(
    name="*",
    datasets=paste(name, collapse=", "),
    n.datasets=n(),
    n.functions=sum(n.functions),
    n.calls=sum(n.calls),
    n.promises=sum(n.promises),
    n.promise.forces=sum(n.promise.forces),
    n.promise.lookups=sum(n.promise.lookups), 
    n.alien.promises=sum(n.alien.promises),
    n.alien.promise.forces=sum(n.alien.promise.forces)
  )

@@

```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
function_types <- load_local_csv("function_types.csv") #FIXME use the concatenated data

@@

```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
closure_function_compilation <- load_local_csv("compiled_functions.csv")

@@

@@

```{r, "function strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
strict_closure_functions <-
  load_local_csv("function_strictness_by_type.csv") %>%
  strictness_labeller

@@

@@

```{r, "call strictness ratios, top 20", echo=FALSE, fig.width=10, fig.height=4.5}
strict_calls_ratio_labelled %>% 
  arrange(desc(number)) %>%
  select(strictness_ratio, number, percent) %>%
  kable(col.names=c( "strictness ratio", "number", "percent"), align="lll")
```

@@

```{r, "function strictness rate", echo=FALSE, fig.width=10, fig.height=4.5}
strict_functions_rate <- load_local_csv("function_strictness_rate.csv")

@@

@@

```{r, "evaluation order", echo=FALSE, fig.width=10, fig.height=4.5}
promise_force_orders <- load_local_csv("evaluation_order.csv")

ggplot(promise_force_orders %>%
      group_by(no.of.force.orders) %>% 
      summarise(number=sum(number)) %>% 
      mutate(percent=100*number/sum(number)), 
    aes(x=no.of.force.orders, y=number)) +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  scale_x_discrete(limit=c(0:10,">10")) +
  theme(legend.position="none") + 
  ylab("No. of functions") +
  xlab("No. of force orders")
```

@@

## Calls to specific functions

>>>>

``` {r, "basic info", include=FALSE}
aggregated_functions <- load_local_csv("aggregated_functions.csv") #

basic_info <- 
  load_local_csv("basic_info.csv") %>%
  group_by(name) %>%
  summarise(
    datasets=paste(name, collapse=", "),
    n.datasets=n(),
    n.functions=sum(n.functions),
    n.calls=sum(n.calls),
    n.promises=sum(n.promises),
    n.promise.forces=sum(n.promise.forces),
    n.promise.lookups=sum(n.promise.lookups), 
    n.alien.promises=sum(n.alien.promises),
    n.alien.promise.forces=sum(n.alien.promise.forces)
  )

@@

aggregate_basic_info <- 
  basic_info %>% summarise(
    name="*",
    datasets=paste(name, collapse=", "),
    n.datasets=n(),
    n.functions=(aggregated_functions %>% count %>% pull(n)),
    n.calls=sum(n.calls),
    n.promises=sum(n.promises),
    n.promise.forces=sum(n.promise.forces),
    n.promise.lookups=sum(n.promise.lookups), 
    n.alien.promises=sum(n.alien.promises),
    n.alien.promise.forces=sum(n.alien.promise.forces)
  )

@@

```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
function_types <- load_local_csv("aggregated_function_types.csv")

@@

```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
closure_function_compilation <- load_local_csv("aggregated_compiled_functions.csv")

@@

```{r, "byte-code compilation, functions loading", echo=FALSE, warning=FALSE}
closure_function_compilation <- load_local_csv("compiled_functions.csv")
```

@@

```{r, "function strictnes", echo=FALSE, fig.width=10, fig.height=4.5}
strict_closure_functions <-
  load_local_csv("aggregated_function_strictness_by_type.csv") %>%
  strictness_labeller

@@

```{r, "function strictnes load", echo=FALSE}
strict_closure_functions <-
  load_local_csv("function_strictness_by_type.csv") %>% 
  strictness_labeller
```

@@

```{r, "call strictness ratios, top 20", echo=FALSE, fig.width=10, fig.height=4.5}
strict_calls_ratio_labelled %>% 
  arrange(desc(number)) %>%
  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
  select(strictness_ratio, number, percent) %>%
  kable(col.names=c( "strictness ratio", "number", "percent"), align="lll")
```

@@

```{r, "function strictness rate", echo=FALSE, fig.width=10, fig.height=4.5}
strict_functions_rate <- load_local_csv("aggregated_function_strictness_rate.csv")

@@

```{r, "function strictness rate load", echo=FALSE}
strict_functions_rate <- load_local_csv("function_strictness_rate.csv")
```

@@

```{r, "evaluation order", echo=FALSE, fig.width=10, fig.height=4.5}
promise_force_orders <- load_local_csv("aggregated_evaluation_order.csv")

all_possible_force_orders <- 
  tibble(no.of.force.orders=c(0:10,">10")) %>% 
  left_join(promise_force_orders %>% mutate(no.of.force.orders=as.character(no.of.force.orders)), by="no.of.force.orders") %>%
  mutate(number=ifelse(is.na(number), 0, number),
         percent=ifelse(is.na(percent), 0, percent))

ggplot(all_possible_force_orders %>%
      group_by(no.of.force.orders) %>% 
      summarise(number=sum(number)) %>% 
      mutate(percent=100*number/sum(number)), 
    aes(x=no.of.force.orders, y=number)) +
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  scale_x_discrete(limit=c(0:10,">10")) +
  theme(legend.position="none") + 
  ylab("No. of functions") +
  xlab("No. of force orders")
```

```{r, "evaluation order load", echo=FALSE}
promise_force_orders <- load_local_csv("evaluation_order.csv")
```

@@

# Calls to specific functions
